### 2018-10-16 Chapters/Chapter2.tex
commit

\begin{align*}
&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right) = \\
 &= \left\{ \right.
	\overbrace{0}^{\uparrow \uparrow \uparrow \uparrow} +
	\overbrace{(-\Delta_{ij}^+)S_i^-(\frac{1}{2}-S_j^z)}^{\uparrow \uparrow \uparrow \downarrow} +
	\overbrace{(-\Delta_{ij}^-)(\frac{1}{2}+ S_i^z)(-S_j^+)}^{\uparrow \uparrow \downarrow \uparrow} +
	\overbrace{2\Delta_{ij}^z S_i^-(-S_j^+)}^{\uparrow \uparrow \downarrow \downarrow} + \\
	&\overbrace{\Delta_{ij}^+ (\frac{1}{2}+S_i^z)(-S_j^-)}^{\uparrow \downarrow \uparrow \uparrow} +
	\overbrace{0}^{\uparrow \downarrow \uparrow \downarrow} +
	\overbrace{0}^{\uparrow \downarrow \downarrow \uparrow} +
	\overbrace{\Delta_{ij}^+ S_i^-(\frac{1}{2}+S_j^z)}^{\uparrow \downarrow \downarrow \downarrow} + \\
	&\overbrace{\Delta_{ij}^- S_i^+(\frac{1}{2}-S_j^z)}^{\downarrow \uparrow \uparrow \uparrow} +
	\overbrace{0}^{\downarrow \uparrow \uparrow \downarrow} +
	\overbrace{0}^{\downarrow \uparrow \downarrow \uparrow} +
	\overbrace{\Delta_{ij}^- (\frac{1}{2} - S_i^z) (-S_j^+)}^{\downarrow \uparrow \downarrow \downarrow} + \\
	& \overbrace{(-2\Delta_{ij}^z)S_i^+(-S_j^-)}^{\downarrow \downarrow \uparrow \uparrow} +
	\overbrace{(-\Delta_{ij}^+) (\frac{1}{2}-S_i^z)(-S_j^-)}^{\downarrow \downarrow \uparrow \downarrow} +
	\overbrace{(-\Delta_{ij}^-) S_i^+(\frac{1}{2}+S_j^z)}^{\downarrow \downarrow \downarrow \uparrow} +
	\overbrace{0}^{\downarrow \downarrow \downarrow \downarrow}
\left. \right\} = \\
&= 2\left\{ \Delta_{ij}^+ (S_i^-S_j^z - S_i^zS_j^-) + \Delta_{ij}^- (S_i^zS_j^+ - S_i^+S_j^z) + \Delta_{ij}^z (S_i^+S_j^- - S_i^-S_j^+) \right\} = \\
&= -2i\left\{ \Delta_{ij}^+ (\bs{S}_i\times\bs{S}_j)^- + \Delta_{ij}^- (\bs{S}_i\times\bs{S}_j)^+ + 2\Delta_{ij}^z (\bs{S}_i\times\bs{S}_j)^z \right\} = -4i \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j 
\end{align*}

@@

\begin{align*}
&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4})\bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\left(-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
&= \dots = \\
&= \begin{pmatrix}
S_i^x & S_i^y & S_i^z
\end{pmatrix}
\\
&\begin{pmatrix}
-2(\Delta_{ij}^z)^2 - 2(\Delta_{ij}^y)^2 + 2(\Delta_{ij}^x)^2 & 4\Delta_{ij}^x\Delta_{ij}^y & 4\Delta_{ij}^x\Delta_{ij}^z \\ 4\Delta_{ij}^y\Delta_{ij}^x & -2(\Delta_{ij}^x)^2+2(\Delta_{ij}^y)^2 -2(\Delta_{ij}^z)^2 & 4\Delta_{ij}^y\Delta_{ij}^z \\ 4\Delta_{ij}^z\Delta_{ij}^x & 4\Delta_{ij}^z\Delta_{ij}^y & -2(\Delta_{ij}^x)^2-2(\Delta_{ij}^y)^2+2(\Delta_{ij}^z)^2
\end{pmatrix}
\\
&\begin{pmatrix}
S_j^x \\ S_j^y \\ S_j^z
\end{pmatrix} = \\
&\sum_{\alpha, \beta} S_i^\alpha (\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta ) S_j^\beta
\end{align*}

>>>>

\begin{align*}
&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
 &= \left\{ \right.
	\overbrace{0}^{\uparrow \uparrow \uparrow \uparrow} +
	\overbrace{(-\Delta_{ij}^+)S_i^-(\frac{1}{2}-S_j^z)}^{\uparrow \uparrow \uparrow \downarrow} +
	\overbrace{(-\Delta_{ij}^-)(\frac{1}{2}+ S_i^z)(-S_j^+)}^{\uparrow \uparrow \downarrow \uparrow} +
	\overbrace{2\Delta_{ij}^z S_i^-(-S_j^+)}^{\uparrow \uparrow \downarrow \downarrow} + \\
	&\overbrace{\Delta_{ij}^+ (\frac{1}{2}+S_i^z)(-S_j^-)}^{\uparrow \downarrow \uparrow \uparrow} +
	\overbrace{0}^{\uparrow \downarrow \uparrow \downarrow} +
	\overbrace{0}^{\uparrow \downarrow \downarrow \uparrow} +
	\overbrace{\Delta_{ij}^+ S_i^-(\frac{1}{2}+S_j^z)}^{\uparrow \downarrow \downarrow \downarrow} + \\
	&\overbrace{\Delta_{ij}^- S_i^+(\frac{1}{2}-S_j^z)}^{\downarrow \uparrow \uparrow \uparrow} +
	\overbrace{0}^{\downarrow \uparrow \uparrow \downarrow} +
	\overbrace{0}^{\downarrow \uparrow \downarrow \uparrow} +
	\overbrace{\Delta_{ij}^- (\frac{1}{2} - S_i^z) (-S_j^+)}^{\downarrow \uparrow \downarrow \downarrow} + \\
	& \overbrace{(-2\Delta_{ij}^z)S_i^+(-S_j^-)}^{\downarrow \downarrow \uparrow \uparrow} +
	\overbrace{(-\Delta_{ij}^+) (\frac{1}{2}-S_i^z)(-S_j^-)}^{\downarrow \downarrow \uparrow \downarrow} +
	\overbrace{(-\Delta_{ij}^-) S_i^+(\frac{1}{2}+S_j^z)}^{\downarrow \downarrow \downarrow \uparrow} +
	\overbrace{0}^{\downarrow \downarrow \downarrow \downarrow}
\left. \right\} = \\
&= 2\left\{ \Delta_{ij}^+ (S_i^-S_j^z - S_i^zS_j^-) + \Delta_{ij}^- (S_i^zS_j^+ - S_i^+S_j^z) + \Delta_{ij}^z (S_i^+S_j^- - S_i^-S_j^+) \right\} = \\
&= -2i\left\{ \Delta_{ij}^+ (\bs{S}_i\times\bs{S}_j)^- + \Delta_{ij}^- (\bs{S}_i\times\bs{S}_j)^+ + 2\Delta_{ij}^z (\bs{S}_i\times\bs{S}_j)^z \right\} = -4i \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j 
\end{align*}

@@

\begin{align*}
&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
&= \overbrace{\Delta_{ij}^z\Delta_{ij}^z(\frac{1}{2}+S_i^z)(\frac{1}{2}-S_j^z)}^{\uparrow \uparrow \uparrow \uparrow} +
	\overbrace{\Delta_{ij}^z\Delta_{ij}^+S_i^-(\frac{1}{2}-S_j^z)}^{\uparrow \uparrow \uparrow \downarrow} +
	\overbrace{\Delta_{ij}^z\Delta_{ij}^-(\frac{1}{2}+ S_i^z)(-S_j^+)}^{\uparrow \uparrow \downarrow \uparrow} +
	\overbrace{\Delta_{ij}^z(-\Delta_{ij}^z) S_i^-(-S_j^+)}^{\uparrow \uparrow \downarrow \downarrow} + \\
	&\overbrace{\Delta_{ij}^+\Delta_{ij}^z (\frac{1}{2}+S_i^z)(-S_j^-)}^{\uparrow \downarrow \uparrow \uparrow} +
	\overbrace{\Delta_{ij}^+\Delta_{ij}^+S_i^-(-S_j^-)}^{\uparrow \downarrow \uparrow \downarrow} +
	\overbrace{\Delta_{ij}^+\Delta_{ij}^-(\frac{1}{2}+S_i^z)(\frac{1}{2}+S_j^z)}^{\uparrow \downarrow \downarrow \uparrow} +
	\overbrace{\Delta_{ij}^+(-\Delta_{ij}^z) S_i^-(\frac{1}{2}+S_j^z)}^{\uparrow \downarrow \downarrow \downarrow} + \\
	&\overbrace{\Delta_{ij}^-\Delta_{ij}^z S_i^+(\frac{1}{2}-S_j^z)}^{\downarrow \uparrow \uparrow \uparrow} +
	\overbrace{\Delta_{ij}^-\Delta_{ij}^+(\frac{1}{2}-S_i^z)(\frac{1}{2}-S_j^z)}^{\downarrow \uparrow \uparrow \downarrow} +
	\overbrace{\Delta_{ij}^-\Delta_{ij}^-S_i^+(-S_j^+)}^{\downarrow \uparrow \downarrow \uparrow} +
	\overbrace{\Delta_{ij}^-(-\Delta_{ij}^z) (\frac{1}{2} - S_i^z) (-S_j^+)}^{\downarrow \uparrow \downarrow \downarrow} + \\
	& \overbrace{(-\Delta_{ij}^z)\Delta_{ij}^z S_i^+(-S_j^-)}^{\downarrow \downarrow \uparrow \uparrow} +
	\overbrace{(-\Delta_{ij}^z)\Delta_{ij}^+ (\frac{1}{2}-S_i^z)(-S_j^-)}^{\downarrow \downarrow \uparrow \downarrow} +
	\overbrace{(-\Delta_{ij}^z)\Delta_{ij}^- S_i^+(\frac{1}{2}+S_j^z)}^{\downarrow \downarrow \downarrow \uparrow} + \\
	&+\overbrace{(-\Delta_{ij}^z)(-\Delta_{ij}^z)(\frac{1}{2}-S_i^z)(\frac{1}{2}+S_j^z)}^{\downarrow \downarrow \downarrow \downarrow} = \\
&= \frac{(\Delta_{ij}^z)^2+\Delta_{ij}^+\Delta_{ij}^-}{2} + S_i^zS_j^z (-2(\Delta_{ij}^z)^2 + 2\Delta_{ij}^+\Delta_{ij}^-) + S_i^zS_j^+(-2\Delta_{ij}^z\Delta_{ij}^-) + S_i^zS_j^-(-2\Delta_{ij}^z\Delta_{ij}^+) +\\ 
&+ S_i^+S_j^z(-2\Delta_{ij}^z\Delta_{ij}^-) + S_i^+S_j^+(-\Delta_{ij}^-\Delta_{ij}^-) + S_i^+S_j^-(\Delta_{ij}^z)^2 +\\
&+ S_i^-S_j^z(-2\Delta_{ij}^z\Delta_{ij}^+) + S_i^-S_j^+(\Delta_{ij}^z)^2 + S_i^-S_j^-(-(\Delta_{ij}^+)^2) = \\
&= \frac{(\Delta_{ij}^z)^2+\Delta_{ij}^+\Delta_{ij}^-}{2} + S_i^zS_j^z(-2(\Delta_{ij}^z)^2+2(\Delta_{ij}^x)^2+2(\Delta_{ij}^y)^2 + S_i^zS_j^y(-4\Delta_{ij}^z\Delta_{ij}^y)+S_i^zS_j^x(-4\Delta_{ij}^z\Delta_{ij}^x) + \\
&+S_i^yS_j^z(-4\Delta_{ij}^y\Delta_{ij}^z)+S_i^yS_j^y(2(\Delta_{ij}^z)^2-2(\Delta_{ij}^y)^2+2(\Delta_{ij}^x)^2)+S_i^yS_j^x(-4\Delta_{ij}^y\Delta_{ij}^x) + \\
&+ S_i^xS_j^z(-4\Delta_{ij}^x\Delta_{ij}^z) + S_i^xS_j^y(-4\Delta_{ij}^x\Delta_{ij}^y) + S_i^xS_j^x(2(\Delta_{ij}^z)^2+2(\Delta_{ij}^y)^2-2(\Delta_{ij}^x)^2) = \\
&= \frac{(\Delta_{ij}^z)^2+\Delta_{ij}^+\Delta_{ij}^-}{2} + \begin{pmatrix}
S_i^x & S_i^y & S_i^z
\end{pmatrix}
\\
&\begin{pmatrix}
2(\Delta_{ij}^z)^2 + 2(\Delta_{ij}^y)^2 - 2(\Delta_{ij}^x)^2 & -4\Delta_{ij}^x\Delta_{ij}^y & -4\Delta_{ij}^x\Delta_{ij}^z \\ -4\Delta_{ij}^y\Delta_{ij}^x & +2(\Delta_{ij}^x)^2-2(\Delta_{ij}^y)^2 +2(\Delta_{ij}^z)^2 & -4\Delta_{ij}^y\Delta_{ij}^z \\ -4\Delta_{ij}^z\Delta_{ij}^x & -4\Delta_{ij}^z\Delta_{ij}^y & 2(\Delta_{ij}^x)^2+2(\Delta_{ij}^y)^2-2(\Delta_{ij}^z)^2
\end{pmatrix}
\begin{pmatrix}
S_j^x \\ S_j^y \\ S_j^z
\end{pmatrix} = \\
&\frac{(\Delta_{ij}^z)^2+\Delta_{ij}^+\Delta_{ij}^-}{2} + \sum_{\alpha, \beta} S_i^\alpha (4\Delta_{ij}^\alpha\Delta_{ij}^\beta - \delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2) S_j^\beta
\end{align*}
